A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-12 archive/v2/docs/discussion_ML_v2.01.tex
Started corrections.

\subsection{On J1331's Stellar Mass-to-Light Ratio} \label{sec:MLdiscussion}

@@

We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec. In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}). We note however, that our results would be much closer to those by \citet{SWELLSV}, if we only used the lensing results at small radii as they did: The total mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ inside the Einstein radius (see Table \ref{tab:einsteinML}). In case of a lower mass dark matter halo, the largest contribution to this mass-to-light ratio would then be stellar mass. And the corresponding IMF would be more bottom-heavy than Salpeter,  like what \citet{SWELLSV} found. The circular velocity curve $v_\text{circ}(R) = \left. sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit). We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$. From this comparison follows, that the model by \citet{SWELLSV} corresponds approximately to a mass-follows-light model in the inner regions of J1331. In Section \ref{sec:results_JAM_SB} however we showed, that this is \emph{not} a good model for J1331 and won't be able to reproduce the central stellar $v_\text{rms}$ dip. On the other hand, because our NFW JAM models fail to predict the stellar kinematics at large radii, the true halo parameters are more likely closer to the findings by \citet{SWELLSV}.\\

>>>>

\subsection{On J1331's stellar mass-to-light ratio} \label{sec:MLdiscussion}

@@

We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec. In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}). We note however, that our results would be much closer to those by \citet{SWELLSV}, if we only used the lensing results at small radii as they did: The total mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ inside the Einstein radius (see Table \ref{tab:einsteinML}). In case of a lower mass dark matter halo, the largest contribution to this mass-to-light ratio would then be stellar mass. And the corresponding IMF would be more bottom-heavy than Salpeter,  like what \citet{SWELLSV} found. The circular velocity curve $v_\text{circ}(R) = \left. \sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit). We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$. From this comparison follows, that the model by \citet{SWELLSV} corresponds approximately to a mass-follows-light model in the inner regions of J1331. In Section \ref{sec:results_JAM_SB} however we showed, that this is \emph{not} a good model for J1331 and won't be able to reproduce the central stellar $v_\text{rms}$ dip. On the other hand, because our NFW JAM models fail to predict the stellar kinematics at large radii, the true halo parameters are more likely closer to the findings by \citet{SWELLSV}.\\
